\section{HOW TO USE}

The usage of the code generator is pretty simple:

\begin{itemize}
\item Since the generator was designed to work better with MagicDraw models,
first create the model with the stereotypes defined in this document, a template
MagicDraw file can be downloded from:\\
http://acsccg.googlecode.com/files/TemplateModelMagicDraw.tar.gz .
\item It is recommended to create a folder with 3 subfolders inside, a
`generated` folder, a `model` folder and a `xmi` folder in which goes the
exported XMI files from MagicDraw.
\item Once the model is defined export the model in : `Eclipse UML2 (v2.x) XMI
FILE` export menu in MagicDraw.
\item Download the Jar Binary from:\\
http://acsccg.googlecode.com/files/ACSCCG.jar
\item Run the generator specifying the model path exported, profile file path
exported and the code path for the code generated:\\ 
\verb+java -jar ACSCCG.jar -model /my/very/path/to/MyProject.uml -profile /my/very/path/to/Alma.profile.uml -output /user/home/MyProject/generated/folder+
\item In the project code page, they are 6 examples of models, image models,
XMI, generated code (tested), ready to download and run, each example represents
a feature of the generator.
\item Update the make file, see the `Knowing Problems` section in this document.
\end{itemize}

\subsection {Generator Command line Help} 
\begin{verbatim}
[atejeda@backorg Desktop]$ java -jar ACSCCG.jar 

ACSCodeGenerator
Compilation 100615

http://code.google.com/p/acsccg/
- Alexis Tejeda <alexis.tejeda@gmail.com>
- Nicolas Troncoso <ntroncos@alma.cl>

usage: java -jar ACSCCG.jar -model /my/very/path/to/MyProject.uml -profile
            /my/very/path/to/Alma.profile.uml -output
            /user/home/MyProject/generated/folder [options]
 -a              About this application
 -c <arg>    True if want to clean the output folder.. ! BEWARE ! will
            erase all from folder an parent folder !
 -h              Print help for this application
 -m <arg>   Model file path, i.e.: /my/very/path/to/MyProject.uml
 -o <arg>   The data source to use
 -p <arg>     Profile UML path, i.e.:
            /my/very/path/to/AlmaGenerator.profile.uml

 An Error has been found, see the help...
                                run: java -jar ACSCCG.jar -h

\end{verbatim}

\subsection {Keep eye on this} 
The generator has an option to clean the directory, this option by default is
disabled, because the output folder can be deleted manually, in case that if
this option is enabled, the generator will delete the destination folder and the
parent folder for the code generated, beware with the paths in case of enable
this option, can cause several damages.

\subsection {Constraints} 
\begin{itemize}
  \item The generator has been tested only with MagicDraw models, but can work
  with other XMI2.x UML models to.
  \item In the model, can exist only one package.
  \item The name of the model has to be in reverse domain name sintax (see the
  examples).
\end{itemize}